\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
\title{Neural Network Approach in Music Source Separation}
\author{Pierre-Louis Guhur }
\date{February 2019}

\begin{document}

\maketitle

\begin{abstract}
    Given a mixture of signals, source separation aims at finding each of the original signal.
    Music is one of the important application field of source separation, as each instrument has a specific signature.
    However, the challenge remains open. Neural networks seem promising to classify short term audio samples among a panel of given instruments.
    A deep analysis of the audio properties provide a clearer understanding of required pre-processing steps.
\end{abstract}

\input{1.Intro.tex}
\input{2.Background.tex}
\input{3.Experiments.tex}
\input{4.Related.tex}


\section{Conclusion}

Since the emergence of deep learning algorithms, music source separation has gained
a strong interest in the literature.
Most of the algorithms are using an STFT representation of the mixture signal,
instead of its waveform.
Predicting the phase is difficult due to discontinuous shape.
However, the phase of the mixture is a correct approximation of each source's phase.
State-of-the-art methods focus then in predicting the magnitude of each source.

In this perspective, the contribution of Muth et al. consists in using phase features
as an input to the DNNs. The phase can not be used directly, but its frequency
and temporal derivatives can help to recover the magnitude of each source signal.
This affirmation relies on an analytical relation between these derivatives and
the magnitude.

In this report, we investigated their contribution, showing how to correct the
distributions of the phase features, but also how to improve the DNN to limit
overfitting. Experiments provided satisfying results, but remained incomplete
for long-term patterns such as fading.


{\small
\bibliographystyle{abbrv}
\bibliography{biblio}
}

\end{document}
